---
title: "LRD paper Appendix C, Data Analysis"
author: "lrd authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

Initialization.
If the variable `paperdir` is supplied, LaTeX code for the tables is saved there, for inclusion in the main paper; otherwise, the code is saved in the current working directory.


```{r setup, include=FALSE,cache=FALSE}
if(!exists('paperdir')) paperdir <- '.'
knitr::opts_chunk$set(echo = TRUE,error=FALSE, warning=FALSE,cache=FALSE,fig.path=paste0(paperdir,'/figure/'))
options(scipen=1, digits=3)
```

General dependencies.
```{r}
#print(getwd())
library('knitr')
library(ggplot2)
library(xtable)
library(robustbase)
library(rdd)
source("R/functions.r")
source("R/data.r")
source("R/ddsandwich.r")
```


```{r load-data,warning=FALSE,message=FALSE}



ciChar <- function(ci,est=FALSE){
    #ci <- round(ci,2)
    ci.out <- paste('(',round2(ci[1]),', ',round2(ci[2]),')',sep='')
    if(est) ci.out <- c(ci.out,as.character(ci[3]))
    ci.out
}

round2 <- function(x) sprintf('%.2f',x)#round(x,2)

nfunc <- function(bw) sum(abs(dat$R)<bw,na.rm=TRUE)

Wfunc <- function(W)
    paste0('[',round2(W[1]), ', ',round2(W[2]),')')


```


Load data. This routine will download and unzip the Lind et al. replication
material into the `extdata` subdirectory.
```{r}
if(!is.element('dat',ls())){
  extdata_dir <- 'extdata'
  LSO_dta_location <- paste0(extdata_dir,'/data_for_analysis.dta')
  if(!file.exists(LSO_dta_location)){
    loc2 <- fetchLSOdata(extdata_dir)
    stopifnot(loc2==LSO_dta_location)
  }
  dat <- foreign::read.dta(LSO_dta_location)
  dat$dist_from_cut <- round(dat$dist_from_cut,2)
  dat$hsgrade_pct[dat$hsgrade_pct==100]=99.5
  dat$lhsgrade_pct=plogis(dat$hsgrade_pct)
  dat$R <- dat$dist_from_cut
  dat$Z <- dat$gpalscutoff
}
```

Total sample size, and number of "compliers" (students whose actual AP
status matched what would have been predicted from first-year GPA)
```{r}
ncomp <- with(dat,sum(gpalscutoff& !probation_year1))
ntot <- nrow(dat)
```

Create RDD plots. First of the outcome (subsequent GPA):
```{r rddFig, fig.height=3.9,fig.width=3.9,dpi=300}

figDat <- aggregate(dat[,c('nextGPA','lhsgrade_pct')],by=list(R=dat$R),
                    FUN=mean,na.rm=TRUE)
figDat$n <- as.vector(table(dat$R))

ggplot(figDat,aes(R,nextGPA,size=n))+
  geom_point()+
  geom_vline(xintercept=0,linetype='dashed',size=1.5)+
  xlab('First-Year GPA (Distance from Cutoff)')+ylab('Avg Subsequent GPA')+
  scale_size_continuous(range=c(0.2,2),guide=FALSE)+
  theme(text = element_text(size=12))
```
then a covariate (High-School GPA):
```{r hs_gpaFig}
ggplot(figDat,aes(R,lhsgrade_pct,size=n))+geom_point()+geom_vline(xintercept=0,linetype='dotted',size=2)+xlab('First-Year GPA (Distance from Cutoff)')+ylab('Avg logit(hsgrade_pct)')+scale_size_continuous(range=c(0.2,2),guide=FALSE)+theme(text = element_text(size=12))

```

The McCrary density test failure and recovery described in Section 4.1
```{r}
(mccrary1 <- rdd::DCdensity(dat$R,-0.005, bin=0.01,plot=FALSE) )
( mccraryDougnut <- rdd::DCdensity(dat$R[dat$R!=0],-0.005, bin=0.01,plot=FALSE) )
```

The Frandsen (2016) test for manipulation when the
running variable is discrete, when the cutoff is the maximum GPA
receiving probation, or the minimum GPA not receiving probation:
```{r}
(frandsen1 <- frandsen(dat$R,cutoff=-0.01,BW=0.5))
(frandsen2 <- frandsen(dat$R,cutoff=0,BW=0.5))
```


## main analysis ##

The sh method uses `lmrob`, which in turn requires a random
seed.  For confidence interval and estimation routines it's
helpful to use the same seed throughout, as this means the
S-estimation initializers will always be sampling the same
subsets of the sample.


```{r main,cache=TRUE}
set.seed(201705)
lmrob_seed <- .Random.seed


SHmain <- sh(subset(dat,R!=0),BW=0.5,outcome='nextGPA',Dvar='probation_year1')
unlist(SHmain)

# No-donut variant (not discussed in text)
SHnodo <- sh(dat, BW=0.5, outcome='nextGPA',Dvar='probation_year1')

SHdataDriven <- sh(dat=subset(dat,R!=0),outcome='nextGPA')
unlist(SHdataDriven)

SHcubic <- sh(dat=subset(dat,R!=0),BW=0.5,outcome='nextGPA',rhs='~Z+poly(R,3)')
unlist(SHcubic)

SHitt <- sh(dat=subset(dat,R!=0),BW=0.5,outcome='nextGPA', Dvar=NULL)
unlist(SHitt) # (AS has no aversion to scatalogical humor)
```

Create Table 1:
```{r table1}

resultsTab <-
 do.call('rbind',
  lapply(list(main=SHmain,data_driven=SHdataDriven,cubic=SHcubic,ITT=SHitt),
   function(res) c(round2(res$CI[3]),
                   ciChar(res$CI[1:2]),
                   W=Wfunc(res$W),
                   n=prettyNum(res$n,',',trim=TRUE))))

colnames(resultsTab) <- c('Estimate','95\\% CI','$\\mathcal{W}$','$n$')



kable(resultsTab)


resultsTab <- cbind(Specification=c('Main','Adaptive $\\mathcal{W}$','Cubic','ITT'),resultsTab)

print(xtable(resultsTab,align='rlcccc'),
  file=paste0(paperdir,"/tab-results.tex"), floating=F,
  include.rownames=FALSE,
  sanitize.colnames.function=function(x) x,
  sanitize.text.function=function(x) x)

```

Results from two alternative methods, creating Table 2:
```{r tabAlt,cache=TRUE}
CFT <- cft(subset(dat,R!=0),BW=NULL,outcome='nextGPA')
IK <- ik(dat,outcome='nextGPA')

altTab <-
 do.call('rbind',
  lapply(list(`Local Linear`=IK,Limitless=SHitt,`Local Permutation`=CFT),
   function(res) c(round2(res$CI[3]),
    ciChar(res$CI[1:2]),
    W=Wfunc(res$W),
    n=prettyNum(res$n,',',trim=TRUE))))



colnames(altTab) <- c('Estimate','95\\% CI','$\\mathcal{W}$','$n$')

kable(altTab)

altTab <- cbind(Method=rownames(altTab),altTab)

print(xtable(altTab,align='rlcccc'),
  file=paste0(paperdir,"/tab-alt.tex"), floating=F,
  include.rownames=FALSE,
  sanitize.colnames.function=function(x) x)

```


## Examine robustness weights

If there are regions of the data of high influence, the robust fitter
should reject or downweight more frequently in those regions, and we'll see dips
on the plot of robustness weights vs R.

Here is the plot corresponding to the main analysis presented in the paper.
```{r weightMod}
lmrob_main <- lmrob(nextGPA~Z+R,
              offset=(SHmain$CI[3]*probation_year1),
              data=dat,subset=(R!=0 & abs(R)<.5),
              method='MM',
              control=lmrob.control(seed=lmrob_seed,
                            k.max=500, maxit.scale=500)
              )
```

Robustness weights are mostly near 1, never below .25.
```{r weightSummary}
robwts_main <- weights(lmrob_main, type="robustness")
summary(robwts_main)
```

Not too much pattern to the robustness weights --
although the lowest values do occur at slightly above
the cutpoint, where we'd see savvy students whose
rose above the cut due to savvyness.

```{r weightPlot, fig.height=3.9,fig.width=3.9,dpi=300}
require(mgcv)
ggp_main <- ggplot(data.frame(R=lmrob_main$model$R,
                              robweights=robwts_main),
                   aes(x=R,y=robweights))
ggp_main + geom_point(alpha=.1) + stat_smooth()+theme(text = element_text(size=12))+ylab('Robustness Weights')
```

When we fit without omitting R=0 students, here is
the best fitting version of the model.

```{r weightNoDonut}
lmrob_nodo <- lmrob(nextGPA~Z+R,
              offset=(SHnodo$CI[3]*probation_year1),
              data=dat,subset=(abs(R)<.5),
              method='MM',
              control=lmrob.control(seed=lmrob_seed,
                                    k.max=500, maxit.scale=500)
      )

robwts_nodo <- weights(lmrob_nodo, type="robustness")
```

Do the observations at R=0 stand out?
With no donut, robustness weights have a slight tendency
to be lower among observations at R=0.

```{r weightNoDonutSummary}
by(robwts_nodo,
   lmrob_nodo$model$R==0, summary)
t.test(wt~atcut, data.frame(wt=robwts_nodo,
                            atcut=(lmrob_nodo$model$R==0)),
       var.equal=F, alternative="g")
```

The plot is similar to that of the main analysis,
with some low robustness weight observations as R=0
but also plenty of ordinary weight observations there.
```{r weightNoDonutPlot}
ggp_nodo <- ggplot(data.frame(R=lmrob_nodo$model$R,
                              robweights=robwts_nodo),
                   aes(x=R,y=robweights))
ggp_nodo + geom_point(alpha=.1) + stat_smooth()
```


Save results:
```{r save}
save(list=ls(),file=paste0('RDanalysis-',format(Sys.time(),"%m%d%H%M"),'.RData'))
```

Session information
```{r}
sessionInfo()
```



