---
title: "Appendix C, Data Analysis"
author: "lrd authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '.')
```

General dependencies.
```{r}
#print(getwd())
library('knitr')
library(ggplot2)
library(xtable)
library(robustbase)
library(rdd)
stopifnot(require('lrd'))
```

Initialization.
```{r load-data,warning=FALSE,message=FALSE}
logit=function(x) log(x*.01/(1-x*.01))


ciChar <- function(ci,est=FALSE){
    ci <- round(ci,2)
    ci.out <- paste('(',round(ci[1],2),',',round(ci[2],2),')',sep='')
    if(est) ci.out <- c(ci.out,as.character(ci[3]))
    ci.out
}

round2 <- function(x) round(x,2)

nfunc <- function(bw) sum(abs(dat$R)<bw,na.rm=TRUE)

Wfunc <- function(W)
    paste0('[',round2(W[1]), ',',round2(W[2]),')')

```


Load data. This routine will download and unzip the Lind et al. replication
material into the `exdata` subdirectory.
```{r}
if(!is.element('dat',ls())){
    if (system.file(package="lrd")!="") {
        extdata_dir <- system.file("extdata", package="lrd")
    } else extdata_dir <- 'extdata'
    LSO_dta_location <- lrd::fetchLSOdata(extdata_dir)
    dat=foreign::read.dta(LSO_dta_location)
                                        #dat=subset(dat,left_school!=1)
    dat$dist_from_cut <- round(dat$dist_from_cut,2)
    dat$hsgrade_pct[dat$hsgrade_pct==100]=99.5
    dat$lhsgrade_pct=logit(dat$hsgrade_pct)
  #dat$age <- dat$age_at_entry>=19
    dat$R <- dat$dist_from_cut
    dat$Z <- dat$gpalscutoff
}
```

Total sample size, and number of "compliers" (students whose actual AP
status matched what would have been predicted from first-year GPA)
```{r}
ncomp <- with(dat,sum(gpalscutoff& !probation_year1))
ntot <- nrow(dat)
```


Create plots for Figure 1. First of the outcome (subsequent GPA):
```{r rddFig}

figDat <- aggregate(dat[,c('nextGPA','lhsgrade_pct')],by=list(R=dat$R),FUN=mean,na.rm=TRUE)
figDat$n <- as.vector(table(dat$R))
figDat <- within(figDat,n <- 2*n/max(n))

with(figDat,plot(R,nextGPA,xlab='First-Year GPA (Distance from Cutoff)',ylab='Avg Subsequent GPA'))
```
then a covariate (High-School GPA):
```{r hs_gpaFig}
with(figDat,plot(R,lhsgrade_pct,xlab='First-Year GPA (Distance from Cutoff)',ylab='Avg logit(hsgrade_pct)'))
```

The McCrary density test failure and recovery described in Section 4.1
```{r}
mccrary1 <- rdd::DCdensity(dat$R,-0.005, bin=0.01,plot=FALSE)
mccraryDougnut <- rdd::DCdensity(dat$R[dat$R!=0],-0.005, bin=0.01,plot=FALSE)
```


## main analysis ##

The sh method uses `lmrob`, which in turn requires a random
seed.  For confidence interval and estimation routines it's
helpful to use the same seed throughout, as this means the
S-estimation initializers will always be sampling the same
subsets of the sample.


```{r}
set.seed(201705)
lmrob_seed <- .Random.seed


SHmain <- lrd::sh(subset(dat,R!=0),BW=0.5,outcome='nextGPA',Dvar='probation_year1')

## No-donut variant (not reported)##
SHnodo <- lrd::sh(dat, BW=0.5, outcome='nextGPA',Dvar='probation_year1')

SHdataDriven <- lrd::sh(dat=subset(dat,R!=0),outcome='nextGPA')

SHcubic <- lrd::sh(dat=subset(dat,R!=0),BW=0.5,outcome='nextGPA',rhs='~Z+poly(R,3)')

SHitt <- lrd::sh(dat=subset(dat,R!=0),BW=0.5,outcome='nextGPA', Dvar=NULL)
```

Create Table 1:
```{r}

resultsTab <-
    do.call('rbind', lapply(list(main=SHmain,data_driven=SHdataDriven,cubic=SHcubic,ITT=SHitt),
                            function(res) c(round2(res$CI[3]),
                                            ciChar(res$CI[1:2]),
                                            W=Wfunc(res$W),
                                            n=res$n)))

colnames(resultsTab) <- c('Estimate','95\\% CI','$\\mathcal{W}$','n')

kable(resultsTab)

print(xtable(resultsTab),
      file="tab-results.tex", floating=F,sanitize.colnames.function=function(x) x)
```

Results from two alternative methods, creating Table 2:
```{r}
CFT <- lrd::cft(subset(dat,R!=0),BW=NULL,outcome='nextGPA')
IK <- lrd::ik(subset(dat,R!=0),outcome='nextGPA')

altTab <-
    do.call('rbind', lapply(list(Limitless=SHitt,`Local Permutation`=CFT,`Local OLS`=IK),
                            function(res) c(round2(res$CI[3]),
                                            ciChar(res$CI[1:2]),
                                            W=Wfunc(res$W),
                                            n=res$n)))



colnames(altTab) <- c('Estimate','95\\% CI','$\\mathcal{W}$','n')

kable(altTab)

print(xtable(altTab),
      file="tab-alt.tex", floating=F,sanitize.colnames.function=function(x) x)
```



```{r}
#' To do: compare robustness weights plots for the next 2 models
lmrob_main <- lmrob(nextGPA~Z+R,
              offset=(SHmain$CI[3]*probation_year1),
              data=dat,subset=(R!=0 & abs(R)<.5),
              method='MM',
              control=lmrob.control(seed=lmrob_seed,
                            k.max=500, maxit.scale=500)
              )

#' Robustness weights are mostly near 1, never below .25.
robwts_main <- weights(lmrob_main, type="robustness")
summary(robwts_main)

#' Not too much pattern to the robustness weights --
#' although the lowest values do occur at slightly above
#' the cutpoint, where we'd see savvy students whose
#' rose above the cut due to savvyness.
ggp_main <- ggplot(data.frame(R=lmrob_main$model$R,
                              robweights=robwts_main),
                   aes(x=R,y=robweights))
ggp_main + geom_point(alpha=.1) + stat_smooth()

#' What were the R values for the lowest-weight points?

subset(ggp_main$data, robweights<.3)


#' When we fit without omitting R=0 students, here is
#' the best fitting version of the model.
lmrob_nodo <- lmrob(nextGPA~Z+R,
              offset=(SHnodo$CI[3]*probation_year1),
              data=dat,subset=(abs(R)<.5),
              method='MM',
              control=lmrob.control(seed=lmrob_seed,
                                    k.max=500, maxit.scale=500)
      )

robwts_nodo <- weights(lmrob_nodo, type="robustness")

#' Do we the observations at R=0 stand out?
#' With no donut, robustness weights have a slight tendency
#' to be lower among observations at R=0.
by(robwts_nodo,
   lmrob_nodo$model$R==0, summary)
t.test(wt~atcut, data.frame(wt=robwts_nodo,
                            atcut=(lmrob_nodo$model$R==0)),
       var.equal=F, alternative="g")


#' The plot is similar to that of the main analysis,
#' with some low robustness weight observations as R=0
#' but also plenty of ordinary weight observations there.
ggp_nodo <- ggplot(data.frame(R=lmrob_nodo$model$R,
                              robweights=robwts_nodo),
                   aes(x=R,y=robweights))
ggp_nodo + geom_point(alpha=.1) + stat_smooth()

#' What were the R values for the lowest-weight points?

subset(ggp_nodo$data, robweights<.3)
```


Save results:
```{r}
save(list=ls(),file=paste0('dataResults/RDanalysis-',format(Sys.time(),"%m%d%H%M"),'.RData'))
```

Session information
```{r}
sessionInfo()
```



