<<<<<<< HEAD
---
title: "Tables from simulations presented in lrd paper"
author: "lrd authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '.')
```

General dependencies.
```{r}
library('knitr')
if(!require('lrd')){
 source("lrd/R/functions.r")
 source("lrd/R/simulations.r")
 source("lrd/R/displaySim.r")
}
```



Initialization. Note that `nreps=0` corresponds to no simulations,
just print results from previously saved simulations.
In order to re-run the simulations, the `nreps`
variable should have been set to a positive integer before initiating this script.

```{r  warning=FALSE, message=FALSE}
if (!exists('nreps') ) nreps <- 0
nreps
if (nreps) {
library('robustbase')
library('rdd')
library('RItools')
library('sandwich')
library('nnet')
source("lrd/R/ddsandwich.R")
set.seed(201609)
st <- system.time(outcomeSim <- lrd:::totalOutcomeSim(nreps))
save(outcomeSim, file="dataResults/outcomeSim.RData")
cat(paste0(date(), ', nreps=', nreps, '\n'),
    paste(c(names(st),'\n', collapse=T)),
    st,
    file='dataResults/fullOutcomeSim-runtime.txt', append=TRUE)
} else load('dataResults/outcomeSim.RData')
```

```{r}
levTab <- lrd:::levels(outcomeSim)
powTab <-lrd:::power(outcomeSim)
capture.output({

cat('
\\begin{table}
\\footnotesize
\\begin{tabular}{cc|ccccccc|cccccc}
\\hline
&&& \\multicolumn{6}{c}{Treatment Effect$=0$}&\\multicolumn{6}{c}{Treatment Effect$=0.2$}\\\\
&&& \\multicolumn{ 2 }{c}{Permutation}&\\multicolumn{ 2 }{c}{\`\`Limitless\'\'}&\\multicolumn{ 2 }{c}{Local OLS}&\\multicolumn{ 2 }{c}{Permutation}&\\multicolumn{ 2 }{c}{\`\`Limitless\'\'}&\\multicolumn{ 2 }{c}{Local OLS}\\\\
$n$& Error &$b=$ &', paste(rep('0.25&0.5',ncol(levTab)),collapse='&'),'\\\\
\\hline \n')
for(i in 1:nrow(levTab)){
    spec <- strsplit(rownames(levTab)[i],' ')[[1]]
    if(spec[1]=='norm'){
        cat('\\hline \n')
        cat('\\multirow{2}{*}{',round(as.numeric(spec[2])),'} & $\\mathcal{N}(0,1)$ &&')
    } else cat(' & $t_3$ &&')
    cat(paste(round(c(levTab[i,],powTab[i,])*100,1),collapse='&'),'\\\\ \n')
}
cat('\\hline
\\end{tabular}
\\caption{Proportion of ',length(outcomeSim[[1]]),' simulations resulting in a p-value below $\\alpha=0.05$ using either permutation tests, limitless or local OLS methods. The left column gives sample sizes with $b=0.5$; the sample size when $b=0.25$ is roughly half the listed $n$ value. When the treatment effect is zero (left) these are empirical estimates of size; otherwise (right), they are estimates of power.}
\\label{tab:level}',sep='')
cat('\\end{table}\n')
},file="lrd/inst/tab-levelSimulation.tex")

kable(levTab,caption = 'Empirical size for hypothesis tests',digits = 2)
kable(powTab,caption = 'Empirical power for hypothesis tests, treatment effect =0.2',digits = 2)

```


The polynomial sim was run in two parts: first for robust regression
and OLS, and next for local linear regression with the IK bandwidth.

```{r  warning=FALSE, message=FALSE}
if (!exists('nreps') ) nreps <- 0
nreps
if (nreps) {
library('robustbase')
library('rdd')
library('RItools')
library('sandwich')
library('nnet')
source("lrd/R/ddsandwich.R")
set.seed(201609)
st2 <- system.time(totalPoly <- lrd:::totalPolySim(nreps))
st3 <- system.time(ikp <- lrd:::totalPolySimIK(nreps))
save(totalPoly,file="dataResults/totalPolySim.RData")
save(ikp,file="dataResults/ikp.RData")
cat(paste0(date(), ', nreps=', nreps, '\n'),
    paste(c(names(st),'\n', collapse=T)),
    st,
    file='dataResults/totalPolySim-runtime.txt', append=TRUE)
} else{
    load('dataResults/totalPolySim.RData')
    load('dataResults/ikp.RData')
    }
```

The following gives the results in Table 4 of the paper, in addition
to the break-down of RMSE into bias and variance, and analogous
results for normally-distributed errors.

```{r}
capture.output(
lrd:::prntTab(totalPoly,ikp,full=FALSE,caption=paste0('Results from ',ncol(totalPoly[[1]]),' simulations of polynomial specifications for RDD analysis, using robust regression and OLS, using all the data, and local linear regression with a triangular kernel and the \\citet{imbens2012optimal} bandwidth. The sample size for all runs was 500, the error distribution was $t_3$, and there was no treatment effect. The data generating models are those depicted in Figure \\ref{fig:dgms}.'),label='tab:poly'),
file="lrd/inst/tab-polynomialSimulation.tex")
kable(prntTab(totalPoly,ikp,full=TRUE,md=TRUE),
      caption='Full results for polynomial simulation',digits=2)
```


Session information
```{r}
sessionInfo()
```
=======
---
title: "LRD paper Appendix D, Simulations invocation and results"
author: "lrd authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '.')
```
# Limitless Regression Discontinuity

## Appendix C, Simulations

General dependencies.
```{r}
#print(getwd())
library('knitr')
if(!require('lrd')){
 source("lrd/R/functions.r")
 source("lrd/R/simulations.r")
 source("lrd/R/displaySim.r")
 source("lrd/R/ddsandwich.R")
}
```



Initialization. Note that `nreps=0` corresponds to no simulations,
just print results from previously saved simulations.
In order to re-run the simulations, the `nreps`
variable should have been set to a positive integer before initiating this script.

```{r  warning=FALSE, message=FALSE}
if (!exists('nreps') ) nreps <- 0
nreps
if (nreps) {
library('robustbase')
library('rdd')
library('RItools')
library('sandwich')
library('nnet')
set.seed(201609)
st <- system.time(outcomeSim <- totalOutcomeSim(nreps))
save(outcomeSim, file="dataResults/outcomeSim.RData")
cat(paste0(date(), ', nreps=', nreps, '\n'),
    paste(c(names(st),'\n', collapse=T)),
    st,
    file='dataResults/fullOutcomeSim-runtime.txt', append=TRUE)
} else load('dataResults/outcomeSim.RData')
```

```{r}
levTab <- levels(outcomeSim)
powTab <- power(outcomeSim)
capture.output({

cat('
\\begin{table}
\\footnotesize
\\begin{tabular}{cc|ccccccc|cccccc}
\\hline
&&& \\multicolumn{6}{c}{Treatment Effect$=0$}&\\multicolumn{6}{c}{Treatment Effect$=0.2$}\\\\
&&& \\multicolumn{ 2 }{c}{Permutation}&\\multicolumn{ 2 }{c}{\`\`Limitless\'\'}&\\multicolumn{ 2 }{c}{Local OLS}&\\multicolumn{ 2 }{c}{Permutation}&\\multicolumn{ 2 }{c}{\`\`Limitless\'\'}&\\multicolumn{ 2 }{c}{Local OLS}\\\\
$n$& Error &$b=$ &', paste(rep('0.25&0.5',ncol(levTab)),collapse='&'),'\\\\
\\hline \n')
for(i in 1:nrow(levTab)){
    spec <- strsplit(rownames(levTab)[i],' ')[[1]]
    if(spec[1]=='norm'){
        cat('\\hline \n')
        cat('\\multirow{2}{*}{',round(as.numeric(spec[2])/2),'} & $\\mathcal{N}(0,1)$ &&')
    } else cat(' & $t_3$ &&')
    cat(paste(round(c(levTab[i,],powTab[i,]),2),collapse='&'),'\\\\ \n')
}
cat('\\hline
\\end{tabular}
\\caption{Proportion of ',length(outcomeSim[[1]]),' simulations resulting in a p-value below $\\alpha=0.05$ using either permutation tests, limitless or local OLS methods. The left column gives sample sizes with $b=0.5$; the sample size when $b=0.25$ is roughly half the listed $n$ value. When the treatment effect is zero (left) these are empirical estimates of size; otherwise (right), they are estimates of power.}
\\label{tab:level}',sep='')
cat('\\end{table}\n')
},file="lrd/inst/tab-levelSimulation.tex")

kable(levTab,caption = 'Empirical size for hypothesis tests',digits = 2)
kable(powTab,caption = 'Empirical power for hypothesis tests, treatment effect =0.2',digits = 2)

```


The polynomial sim was run in two parts: first for robust regression
and OLS, and next for local linear regression with the IK bandwidth.

```{r  warning=FALSE, message=FALSE}
if (!exists('nreps') ) nreps <- 0
nreps
if (nreps) {
library('robustbase')
library('rdd')
library('RItools')
library('sandwich')
library('nnet')
set.seed(201609)
st2 <- system.time(totalPoly <- totalOutcomeSim(nreps))
st3 <- system.time(ikp <- totalPolySimIK(nreps))
save(totalPoly,file="dataResults/totalPolySim.RData")
save(ikp,file="dataResults/ikp.RData")
cat(paste0(date(), ', nreps=', nreps, '\n'),
    paste(c(names(st),'\n', collapse=T)),
    st,
    file='dataResults/totalPolySim-runtime.txt', append=TRUE)
} else{
    load('dataResults/totalPolySim.RData')
    load('dataResults/ikp.RData')
    }
```

The following gives the results in Table 4 of the paper, in addition
to the break-down of RMSE into bias and variance, and analogous
results for normally-distributed errors.

```{r}
capture.output(
prntTab(totalPoly,ikp,full=FALSE,caption=paste0('Results from ',ncol(totalPoly[[1]]),' simulations of polynomial specifications for RDD analysis, using robust regression and OLS, using all the data, and local linear regression with a triangular kernel and the \\citet{imbens2012optimal} bandwidth. The sample size for all runs was 500, the error distribution was $t_3$, and there was no treatment effect. The data generating models are those depicted in Figure \\ref{fig:dgms}.'),label='tab:poly'),
file="lrd/inst/tab-polynomialSimulation.tex")
kable(prntTab(totalPoly,ikp,full=TRUE,md=TRUE),
      caption='Full results for polynomial simulation',digits=2)
```


Session information
```{r}
sessionInfo()
```
>>>>>>> origin/master
