---
title: "Tables from simulations presented in lrd paper"
author: "lrd authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,error=FALSE)
knitr::opts_knit$set(root.dir = '.')
```

General dependencies.
```{r}
library('knitr')
#library('lrd')
library('kableExtra')
source('R/simCIhet.r')
source('R/functions.r')
source('R/ddsandwich.R')
source('R/displaySim.r')
```



Initialization. Note that `nreps=0` corresponds to no simulations,
just print results from previously saved simulations.
In order to re-run the simulations, the `nreps`
variable should have been set to a positive integer before initiating this script.

##Level/Power Simulation
The following code (optionally, if `nreps>0`) runs the simulation
reported in Table 3 of "Limitless Regression Discontinuity"

To run the simulations in parallel, using the `parallel` package in
`R`,
register a cluster, called `cl` with the desired number of nodes, with
code similar to the following:
```{r eval=FALSE,echo=TRUE}
library(parallel)
cl <- makeCluster(5)
```

```{r  runLoadOutSim, warning=FALSE, message=FALSE}
if (!exists('nreps') ) nreps <- 0
nreps
if (nreps) {
library('robustbase')
library('rdd')
library('RItools')
library('sandwich')
library('nnet')

if(require('parallel')&exists('cl')&inherits(cl,"cluster")){
  clusterEvalQ(cl,{
             library('robustbase')
             library('rdd')
             library('RItools')
             library('sandwich')
             library('nnet')
             source('R/functions.r')
             source('R/simCIhet.r')
             })
} else cl <- NULL

set.seed(201609)
st <- system.time(outcomeSim <- totalOutcomeSim(nrep,cl))
save(outcomeSim, file=paste0('inst/outcomeSim',Sys.Date(),'.RData'))
cat(paste0(date(), ', nreps=', nreps, '\n'),
    paste(c(names(st),'\n', collapse=T)),
    st,
    file='dataResults/fullOutcomeSim-runtime.txt', append=TRUE)
} else{ ### load the most recent simulation
  sims <- sort(grep('outcomeSim',list.files('./inst/'),value=TRUE),decreasing=TRUE)

  load(paste0('inst/',sims[1]))
}
```

This code creates Table 3:
```{r table3}
capture.output({
  displayCIsimHet(outcomeSim,tau=0,
    caption=paste('Empirical bias and 95\\% confidence interval coverage and width for the analyses of ',ncol(outcomeSim[[1]]),'simulated datasets using either permutation tests, limitless or local OLS methods. The average treatment effect was zero in all conditions; in six conditions the effect was uniquely zero, and in three it was distributed as $t_3$.'),
    label='tab:level')
  },file="inst/r1/tab-levelSimulation.tex")
```
Here are the results, for all cases run:

```{r fullOutSim}
allRes <- dispAllSimp(outcomeSim)
rownames(allRes) <- NULL
save(allRes,file=paste0('inst/levelSimResults',Sys.Date(),'.RData'))
```

###Full Results: Bias
```{r biasTab}
kable(subset(allRes,meas=='Bias',select=-meas),caption=paste('Empirical bias for the analyses of ',ncol(outcomeSim[[1]]),'simulated datasets using either permutation tests, limitless or local OLS methods. Results for all conditions'),digits=2,format='html')%>%
  kable_styling(full_width=FALSE)%>%
#  group_rows("n=50",1,24)%>%group_rows("n=250",25,48)%>%group_rows("n=2500",49,72)%>%
  collapse_rows(columns = 1:4)#, valign = "center")
```

###95% CI Coverage
```{r coverTab}
kable(subset(allRes,meas=='Coverage',select=-meas),caption=paste('Empirical 95% confidence interval coverage for the analyses of ',ncol(outcomeSim[[1]]),'simulated datasets using either permutation tests, limitless or local OLS methods. Results for all conditions'),digits=2,format='html')%>%
  kable_styling(full_width=FALSE)%>%
#  group_rows("n=50",1,24)%>%group_rows("n=250",25,48)%>%group_rows("n=2500",49,72)%>%
  collapse_rows(columns = 1:4)#, valign = "center")
```

###95% CI Width
```{r widthTab}
kable(subset(allRes,meas=='Width',select=-meas),caption=paste('Empirical 95% confidence interval width for the analyses of ',ncol(outcomeSim[[1]]),'simulated datasets using either permutation tests, limitless or local OLS methods. Results for all conditions'),digits=2,format='html')%>%
  kable_styling(full_width=FALSE)%>%
#  group_rows("n=50",1,24)%>%group_rows("n=250",25,48)%>%group_rows("n=2500",49,72)%>%
  collapse_rows(columns = 1:4)#, valign = "center")
```



##Polynomial Simulation

```{r  runLoadPolySim, warning=FALSE, message=FALSE}
if (!exists('nreps') ) nreps <- 0
nreps
if (nreps) {


set.seed(201609)
st2 <- system.time(totalPoly <- totalPolySim(nreps,cl))
save(totalPoly,file=paste0("inst/totalPolySim",Sys.Date(),".RData"))
cat(paste0(date(), ', nreps=', nreps, '\n'),
    paste(c(names(st),'\n', collapse=T)),
    st,
    file='dataResults/totalPolySim-runtime.txt', append=TRUE)
} else{
  psims <- sort(grep('totalPolySim',list.files('./inst/'),value=TRUE),decreasing=TRUE)

  load(paste0('inst/',psims[1]))
}
```

The following gives the results in Table 4 of the paper, in addition
to the break-down of RMSE into bias and variance, and analogous
results for normally-distributed errors.

```{r}
tab.paper <- prntTab(totalPoly,5,full=FALSE,md=FALSE)
capture.output(
polyLatex5(tab.paper,full=FALSE,caption=paste0('Results from ',ncol(totalPoly[[1]]),' simulations of polynomial specifications for RDD analysis, using MM-estimation, OLS or local linear regression. Data generating models were as depicted in Figure~\\ref{fig:dgms}, with $t_{3}$ errors; sample size for all runs was 500, and there was no treatment effect.'),label='tab:poly'),
    file="inst/r1/tab-polynomialSimulation.tex")

tab <- prntTab(totalPoly,5,full=TRUE,md=FALSE)
#rownames(tab) <- rep(c('level','RMSE','bias','sd'),6)
colnames(tab) <- gsub('(sh|ik)\\.est.','deg=',colnames(tab))#c(rep(paste0('deg=',1:4),2),'')
colnames(tab)[ncol(tab)] <- 'n/a'
kable(tab,format='html',caption='Full results for polynomial simulation',digits=2)%>%
    kable_styling()%>% column_spec( 6,border_right=TRUE)%>%column_spec(11,border_right=TRUE)%>%
        add_header_above(c(" " = 1, "Limitless" = 5, "OLS" = 5, "Loc. Lin." = 1))%>%
            #group_rows("$t_3$ Error",1,12)%>%group_rows("N(0,1) Error",13,24)%>%
            group_rows("linear",1,3)%>%group_rows('antiSym',4,6)%>%group_rows('sine',7,9)#%>%
                #group_rows("linear",13,16)%>%group_rows('antiSym',17,20)%>%group_rows('oneSide',21,24)
```


Session information
```{r}
sessionInfo()
```
